Global adjoint tomography -- Model GLAD-M25\footnote{This paper is dedicated to Dimitri Komatitsch, computational geophysicist extraordinaire, who passed away unexpectedly shortly before its submission.}

### 2020-02-11 main.tex
fix issues in figures as suggested by Jeroen
Updates from Overleaf

Figure~\ref{fig:??} shows the results of the four PSF tests we performed for model GLAD-M25.
The first test repeats an analysis performed by~\cite{bozdaug2016global} for GLAD-M15 in the upper mantle underneath Yellowstone.
That test was based on 253 earthquakes,
and Figures~\ref{fig:??}a and~\ref{fig:??}b show our results for the same location based on half our dataset (720 events) and the full dataset (1,480 events), respectively.
Figure~\ref{fig:??} shows the results of a PSF test in the lowermost mantle at the base of the African superplume,
in the lower mantle beneath the Galapagos,
and in the mid mantle below Indonesia.

@@

Relative to our first generation model GLAD-M15,
we observe a significant increase in model perturbation amplitudes and resolution,
both in the upper and lower mantle.
To illustrate this point,
Fig.~\ref{fig:power} and Fig.~\ref{fig:powerspectraradius} show normalized power per angular degree (Eqn.~\ref{eq:powerdegree}) and normalized power per angular degree as a function of radius (Eqn.~\ref{eq:powerdegreeradius}), respectively, for models S362ANI, GLAD-M15, and GLAD-M25.
Model S362ANI has no power beyond degree~18,
and we see and increase in power for GLAD-M25 relative to GLAD-M15 beyond degree~10.

@@

Fig.~\ref{fig:M24-Iceland} showcases the north Atlantic, where we see clear expressions of the Jan Mayen and Iceland plumes as well as the Azores, Canary Islands, and Bermuda.

@@

Figure~\ref{fig:global-average} shows the resulting radial averages of the isotropic shear and compressional wavespeeds for model~GLAD-M25
compared to 1D starting model~STW105~\citep{kustowski2008anisotropic} and PREM~\citep{PREM}.
The radial average of~GLAD-M25 remains very close to the radial starting model~STW105.
The main difference between these two models and~PREM
is the absence of the 220~km discontinuity and a lower~$V_\text{P}/V_\text{S}$ ratio in the top 200~km.

>>>>

Fig.~\ref{fig:??} shows the results of the four PSF tests we performed for model GLAD-M25.
The first test repeats an analysis performed by~\cite{bozdaug2016global} for GLAD-M15 in the upper mantle underneath Yellowstone.
That test was based on 253 earthquakes,
and Figs.~\ref{fig:??}a and~\ref{fig:??}b show our results for the same location based on half our dataset (720 events) and the full dataset (1,480 events), respectively.
We observe that the 75~km diameter anomaly is well recovered, with little tradeoff.
Figs.~\ref{fig:??}c--f shows the results of PSF tests in the lowermost mantle at the base of the African superplume,
in the lower mantle beneath the Galapagos,
and in the mid mantle below Indonesia.
In each case the Gaussian anomaly is well recovered, with minimal tradeoff with other model parameters.

@@

Relative to our first generation model GLAD-M15,
we observe a significant increase in model perturbation amplitudes and resolution,
both in the upper and lower mantle.
To illustrate this point,
Fig.~\ref{fig:power} and Fig.~\ref{fig:powerspectraradius} show normalized power per angular degree (Eqn.~\ref{eq:powerdegree}) and normalized power per angular degree as a function of radius (Eqn.~\ref{eq:powerdegreeradius}), respectively, for models S362ANI, GLAD-M15, and GLAD-M25.
Model S362ANI has no power beyond degree~18,
and we see and increase in power for GLAD-M25 relative to GLAD-M15 beyond degree~10 throughout the mantle.

@@

Fig.~\ref{fig:M24-Iceland} showcases the north Atlantic, where we see clear expressions of the Jan Mayen and Iceland plumes as well as the Azores, Canary Islands, and Bermuda,
and Fig.~\ref{fig:M24-Reunion} shows the emergence of hotspots in the Indian Ocean in model Glad-M25,
including Marion, Crozet, Kerguelen, Cocos, R\'eunion, and Seychelles.

@@

Fig.~\ref{fig:global-average} shows the resulting radial averages of the isotropic shear and compressional wavespeeds for model~GLAD-M25
compared to 1D starting model~STW105~\citep{kustowski2008anisotropic} and PREM~\citep{PREM}.
The radial average of~GLAD-M25 remains very close to the radial starting model~STW105.
The main difference between these two models and~PREM
is the absence of the 220~km discontinuity and a lower~$V_\text{P}/V_\text{S}$ ratio in the top 200~km.
